The impact of cosmic variance on simulating weak lensing surveys

### 2014-12-01 Writeup/paper_v3.tex
do not make text disappear
soften statements re: Semboloni comparison

%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
\newcommand{\rachel}[1]{}
\newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
%\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{magenta}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\rachel{The estimates in this subsection are rough illustrations of
  the magnitudes of these effects.  Other aspects of shear calibration
  that could be affected relate to the use of {\em HST} data to
  estimate the impact of detailed galaxy morphology, or to calibrate
  the effect of colour gradients
  \citep{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.  In the latter
  case, what is most relevant in this work is our finding that $B/T$
  exhibits environmental dependence, which likely translates into
  environmental dependence of colour gradients.  Unfortunately, we
  cannot directly test the strength of any colour gradient variations
  with environment using COSMOS data, due to the fact that there is
  only single-band coverage in much of its area.  We note that our
  findings may seem to be at odds with the conclusions in
  \cite{2013MNRAS.432.2385S} based on synthetic galaxy models that the
  existing area of {\em HST} coverage with $\ge 2$ bands is sufficient
  for calibration of colour
  gradients \rachelnew{ as a function of galaxy type}\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
    fluctuations in colour gradients within the source galaxy sample
    in the Euclid weak lensing survey due to environmental effects
    will not be a significant source of uncertainty.  However, the
    question addressed in that work is different from the question
    considered here, which is the impact of fluctuations in colour
    gradients in the training sample used to derive the corrections,
    rather than in the galaxy sample to which those corrections will
    be applied.}}.  This is particularly striking given that, as shown
  there, the dominant galaxy sample with $2$-band coverage is the
  AEGIS dataset, which has substantially smaller area than COSMOS, and
  therefore should exhibit a stronger influence of cosmic variance.
  \rachelnew{The presence of other fields besides AEGIS (e.g., GOODS)
    should help mitigate this effect given that the large-scale
    structure in the two fields will be completely uncorrelated, but
    the number of fields is still not large and the area is dominated
    by a small number of them\footnote{\rachelnew{For context,
        \cite{2015APh....63...81N} 
        showed that for tests of photometric redshift quality, the
        number of spectroscopic fields of this size that would be
        required for future surveys to avoid the influence of cosmic
        variance ranges from many tens to hundreds}}.}  It seems that a future study using
  an {\em HST} field with more than one band would be warranted, to
  test whether the discrepancy between our findings and those of
  \cite{2013MNRAS.432.2385S} arises from a weak connection between
  colour gradients and $B/T$ (meaning that our results do not imply a
  problem with colour gradient calibration), or from some unrealistic
  aspect to the synthetic models used in that work.}

>>>>

%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
\newcommand{\rachel}[1]{#1}
\newcommand{\rachelnew}[1]{{\textcolor{red}{#1}}}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
%\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{magenta}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\rachel{The estimates in this subsection are rough illustrations of
  the magnitudes of these effects.  Other aspects of shear calibration
  that could be affected relate to the use of {\em HST} data to
  estimate the impact of detailed galaxy morphology, or to calibrate
  the effect of colour gradients
  \citep{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.  In the latter
  case, what is most relevant in this work is our finding that $B/T$
  exhibits environmental dependence, which likely translates into
  environmental dependence of colour gradients.  Unfortunately, we
  cannot directly test the strength of any colour gradient variations
  with environment using COSMOS data, due to the fact that there is
  only single-band coverage in much of its area.  We note that our
  findings may seem to be at odds with the conclusions in
  \cite{2013MNRAS.432.2385S} based on synthetic galaxy models that the
  existing area of {\em HST} coverage with $\ge 2$ bands is sufficient
  for calibration of colour
  gradients\footnote{\rachel{\cite{2012MNRAS.421.1385V} showed that the
    fluctuations in colour gradients within the source galaxy sample
    in the Euclid weak lensing survey due to environmental effects
    will not be a significant source of uncertainty.  However, the
    question addressed in that work is different from the question
    considered here, which is the impact of fluctuations in colour
    gradients in the training sample used to derive the corrections,
    rather than in the galaxy sample to which those corrections will
    be applied.}}.  This is particularly striking given that, as shown
  there, the dominant galaxy sample with $2$-band coverage is the
  AEGIS dataset, which has substantially smaller area than COSMOS, and
  therefore should exhibit a stronger influence of cosmic variance.
  \rachelnew{The presence of other fields besides AEGIS (e.g., GOODS)
    should help mitigate this effect given that the large-scale
    structure in the two fields will be completely uncorrelated, but
    the number of fields is still not large and the area is dominated
    by a small number of them\footnote{\rachelnew{For context,
        \cite{2015APh....63...81N} 
        showed that for tests of photometric redshift quality, the
        number of spectroscopic fields of this size that would be
        required for future surveys to avoid the influence of cosmic
        variance ranges from many tens to hundreds}}.}

\rachelnew{However, it is important to bear in mind that the method
  proposed in \cite{2013MNRAS.432.2385S} involves determining not just
a redshift-dependent correction but also a type-dependent colour
gradient correction, which could partially mitigate the effects of the
environment dependence seen here.  We showed in
Sec.~\ref{sec:mitigation} that a simple type-dependent split does not
remove the effects of environment on the intrinsic ellipticity
distribution, but testing whether it (or a more complex type split) is
enough to remove the effects of colour gradients in Euclid is a more
complicated analysis that is beyond the scope of this work.} It seems that a future study using
  an {\em HST} field with more than one band would be warranted, to
  test whether the \rachelnew{ possible} discrepancy between our findings and those of
  \cite{2013MNRAS.432.2385S} arises from a weak connection between
  colour gradients and $B/T$ (meaning that our results do not imply a
  problem with colour gradient calibration), \rachelnew{or whether a
    division into several galaxy types is truly enough to remove the colour
    gradient effect, verifying the conclusions of
    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}
